Exception Handling Bug Hazards in Android

### 2015-10-07 SPRINGER_JOURNAL/msr_journal.tex
survey section

%///// HANDLING RUNTIME AND CHECKED /////		
To acess developers perspective on whether checked and unchecked exceptions should be handled different inside the app, the developers were presented to two pieces of code: one on which a RuntimeException was caught and another one where an IOException has caught; both in the contexts of Activity life-cycle methods. Then the developers were asked whether or not the way to handle a runtime exception should be different from the way to handle a checked exception.

@@

The goal of this paper is two-fold: (i) to investigate 
to what extent stack trace information can reveal \emph{bug hazards} 
related to exception handling code that may lead to a decrease in
application robustness; and (ii) investigate the developers perspective
concerning the detected EH \emph{bug hazards}.

>>>>

%///// HANDLING RUNTIME AND CHECKED /////		
To assess developers perspective on whether checked and unchecked exceptions should be handled different inside the app, the developers were presented to two pieces of code: one on which a RuntimeException was caught and another one where an IOException has caught; both in the contexts of Activity life-cycle methods. Then the developers were asked whether or not the way to handle a runtime exception should be different from the way to handle a checked exception.

@@

The goal of this paper is two-fold: (i) to investigate 
to what extent stack trace information can reveal \emph{bug hazards} 
related to exception handling code that may lead to a decrease in
application robustness; and (ii) to assess the developers perspective
concerning the detected EH \emph{bug hazards}.
